### 2020-01-31 ChapterConclusion/chapterConclusion.tex
Updated: More re-writing of conclusion

The use of modern cloud technologies will also be researched, such as containers and container orchestration in order to facilitate efficient provisioning and management of additional compute resources within a distributed physics simulation. The use of lightweight containers versus virtual machine instances may allow for more precise control of compute resource allocation and faster on-demand provisioning, which would lend itself well to streamed gaming applications.

>>>>

The use of containers, such as Docker, for the deployment of AP could also be investigated and compared with the current implementation that uses virtual machine cloud instances. Containers would allow for efficient provisioning and management of compute resources within the system as they enable more precise control over resources allocated. In addition, containers provide faster on-demanding provisioning of resources. Using containers instead of cloud instances may require additional overhead in terms of performance, which could be investigated and the trade-off between cloud instances and the benefits of containers explored.
%The use of modern cloud technologies will also be researched, such as containers and container orchestration in order to facilitate efficient provisioning and management of additional compute resources within a distributed physics simulation. The use of lightweight containers versus virtual machine instances may allow for more precise control of compute resource allocation and faster on-demand provisioning, which would lend itself well to streamed gaming applications.
